<!DOCTYPE HTML>
<!--
	Spectral by HTML5 UP
	html5up.net | @ajlkn
	Free for personal and commercial use under the CCA 3.0 license (html5up.net/license)
-->
```{r Packages, message=FALSE, warning=FALSE, echo=TRUE, results='hide'}
library(leaflet)
library(mapdata)
library(maptools)
library(tidyverse)
library(cowplot)
library(maps)
```

<html>
	<head>
		<title>Education</title>
		<meta charset="utf-8" />
		<meta name="viewport" content="width=device-width, initial-scale=1, user-scalable=no" />
		<link rel="stylesheet" href="assets/css/main.css" />
		<noscript><link rel="stylesheet" href="assets/css/noscript.css" /></noscript>
	</head>
	<body class="is-preload">

		<!-- Page Wrapper -->
			<div id="page-wrapper">

				<!-- Header -->
					<header id="header">
						<h1><a href="index.html">Education</a></h1>
						<nav id="nav">
							<ul>
<li class="special">
									<a href="#menu" class="menuToggle"><span>Navigation</span></a>
									<div id="menu">
										<ul>
											<li><a href="index.html">Home</a></li>
											<li><a href="education.html">Education</a></li>
											<li><a href="work.html">Work</a></li>
											<li><a href="research.html">Research</a></li>
											<li><a href="photography.html">Photography</a></li>
							       	<li><a href="https://tigereyeartstudio.weebly.com/">Art & Illustration</a></li>
											<li><a href="contact.html">Contact</a></li>
										</ul>
									</div>
								</li>
							</ul>
						</nav>
					</header>

				<!-- Main -->
					<article id="main">
						<section class="wrapper style5">
							<div class="inner">

								<h3>Master’s of Science in Biology</h3>
								<h5>2020-2022 - In progress (24/32 credits completed)</h5>
								<p><b><a href="https://www.apsu.edu/">Austin Peay State University</a></b>, Clarksville, TN<br />
GPA: 3.75/4.0</p>

								<hr />
								

```{r, fig.align="center"}
apsu <- data.frame("x" = -86.905274, "y" = 36.269134)
rotary_point <- data.frame("x" = -87.271600, "y" = 36.501317)
cheatham_point <- data.frame("x" = -87.063088, "y" = 36.188858)
schiller_point <- data.frame("x" = -87.314360, "y" = 36.437066)
```

```{r Map, fig.align="center", echo=FALSE}
leaflet(apsu) %>% 
  addTiles() %>%
  addProviderTiles(providers$CartoDB.Positron, group = "CartoDB") %>%
  addProviderTiles(providers$Esri.NatGeoWorldMap, group = "NatGeo") %>%
  addProviderTiles(providers$Esri.WorldImagery, group = "ESRI") %>%
    setView(lng = -86.917820, lat = 36.259360, zoom = 16) %>%
  addCircleMarkers(popup = lowaOGR@data$Description,
                   label = lowaOGR@data$Name,
                   weight = 2,
                   color = "white",
                   fillColor = "green",
                   fillOpacity = 0.9) %>%
  addMiniMap(zoomLevelOffset = -4, width = 100, height = 120)  %>%
  addLayersControl(
    baseGroups = c("ESRI", "NatGeo", "OSM", "CartoDB"),
    options = layersControlOptions(collapsed = FALSE),
    overlayGroups = "Beaman Park")
```

```{r interactive apsu, message=FALSE, warning=FALSE, echo=TRUE, results='hide'}
pal <- colorBin(c("#fa815d", "#f28c11", "#f3e811", "#a8ef28", "#00bc17", "#003607"), caro_rgbif_df$year)

leaflet(ivory_rgbif_df) %>% 
  addTiles() %>% 
    setView(lng = -87.392613, lat = 35.390011, zoom = 4) %>%
  addCircleMarkers(caro_rgbif_df$x,
                   caro_rgbif_df$y,
                   popup = caro_rgbif_df$species,
                   label = caro_rgbif_df$year,
                   color = ~pal(year),
                   weight = 1,
                   fillOpacity = 0.7) %>%
  addMiniMap(position = 'topright',
             width = 100, 
             height = 100,
             toggleDisplay = FALSE) %>%
  addScaleBar(position = "bottomright") %>%
  addLegend("bottomleft", pal = pal, values = ~caro_rgbif_df$year,
    title = "Year Seen",
    labFormat = labelFormat(),
    opacity = 1)

```

								<h3>B.A. Biology</h3>
<h5>2014-2018</h5>
<p><b><a href="https://calvin.edu/">Calvin University</a></b>, Grand Rapids, MI<br />
Minor in Studio Art<br />
GPA: 3.4/4.0</p></p>

								<hr />

<h5>2011-2014</h5>
<p><b><a href="https://www.kellogg.edu/">Kellogg Community College</a></b>, Battle Creek, MI<br />
GPA: 3.9/4.0</p></p>

							</div>
						</section>
					</article>

				<!-- Footer -->
					<footer id="footer">
						<ul class="icons">
							<li><a href="https://ebird.org/profile/MTE3NzY3OQ/world" class="fas fa-crow"></a></li>
							<li><a href="https://www.instagram.com/birds_in_hand/" class="icon brands fa-instagram"><span class="label">Instagram</span></a></li>
							<li><a href="https://www.linkedin.com/in/jenna-atma-a93178113/" class="icon brands fa-linkedin"><span class="label">LinkedIn</span></a></li>
							<li><a href="https://github.com/jatmasphere/" class="icon brands fa-github"><span class="label">GitHub</span></a></li>
							<li><a href="contact.html" class="icon solid fa-envelope"><span class="label">Email</span></a></li>
						</ul>
						<ul class="copyright">
							<li>&copy; Jenna Atma</li><li>Design: <a href="http://html5up.net">HTML5 UP</a></li>
						</ul>
					</footer>

			</div>

		<!-- Scripts -->
			<script src="assets/js/jquery.min.js"></script>
			<script src="assets/js/jquery.scrollex.min.js"></script>
			<script src="assets/js/jquery.scrolly.min.js"></script>
			<script src="assets/js/browser.min.js"></script>
			<script src="assets/js/breakpoints.min.js"></script>
			<script src="assets/js/util.js"></script>
			<script src="assets/js/main.js"></script>

	</body>
</html>